Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}

```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}

```

***

### Overplotting
Notes:

ggplot(aes(x = age, y = friend_count), data = pf) +  ## Scatterplot
  geom_jitter(alpha = 1/20) +  
  xlim(13,90)

## Instead of using geom_point use geom_jitter to see the data more accuratley since it creates more noize

#### What do you notice in the plot?
Response:

Age group between 13 and 25 has many more freinds than most of the other ages and we see a thin line except at 60 which is unusual

### Coord_trans()
Notes:


  

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

  ggplot(aes(x = age, y = friend_count), data = pf) +  ## Scatterplot
  geom_point(alpha = 1/20) +
  xlim(13,90) +
  coord_trans(y = 'sqrt')
  
#### What do you notice?

***

### Alpha and Jitter
Notes:

ggplot(aes(x = age, y = friendships_initiated), data = pf) +  ## Scatterplot
  geom_point(alpha = 1/20 , position = position_jitter(h = 0)) +
  scale_x_continuous(breaks = seq(10, 120, 10)) +
  coord_trans(y = 'sqrt') 
***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

pf.fc_by_age <- pf %>% 
  group_by(age) %>%
  summarise(friend_count_mean  = mean(friend_count),
            friend_count_median  = median(friend_count),
            n = n()) %>% 
  arrange(age)

Create your plot!

ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) +  ## line Graph
  geom_line() 

***

### Overlaying Summaries with Raw Data
Notes:

ggplot(aes(x = age, y = friend_count), data = pf) +  ## Overlaying summaries 
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = 'orange') +
  xlim(13,90) +
  coord_trans(y = 'sqrt') +
  geom_line(stat = 'summary', fun.y = mean)

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with( subset(pf , age <=70) , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

